---
title: "Project_Gelly_Auto"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Scope of work**

Chinese automobile company Geely Auto wants to setup a manufacturing unit
in US so that it can compete in US and Europe markets.
They want to know on which factors the price depends.
Primarily it wants to know which variables are significant in predicting the price of car
and how well they describe the price of car.

**Data Dictionary**

**Variable Name -- Variable Desc -- Variable Type**

* Car_ID - Unique id - Interger
* Symboling - Insurance risk rating, A value of +3 indicates that the auto is risky, -3 that it is probably pretty safe. - Categorical
* carCompany - Name - Categorical
* fueltype - Fuel type - Categorical
* aspiration - Aspiration used in a car - Categorical
* doornumber - No. of doors - Categorical
* carbody - Body of car - Categorical
* drivewheel - Type of drive wheel - Categorical
* enginelocation - Location of car engine - Categorical
* wheelbase - Weelbase of car - Numeric
* carlength - Length of car - Numeric
* carwidth - Width of car - Numeric
* carheight - Height of car - Numeric
* curbweight - The weight of a car without occupants or baggage. - Numeric
* enginetype - Type of engine. - Categorical
* cylindernumber - Cylinder placed in the car - Categorical
* enginesize - Size of car - Numeric
* fuelsystem - Fuel system of car - Categorical
* boreratio - Boreratio of car - Numeric
* stroke - Stroke or volume inside the engine - Numeric
* compressionratio - compression ratio of car - Numeric
* horsepower - Horsepower - Numeric
* peakrpm - Car peak rpm - Numeric
* citympg - Mileage in city - Numeric
* highwaympg - Mileage on highway - Numeric
* price - Price of car-Numeric - To be Predicted

Setting up the working directory and loading car price file to R console

```{r}
setwd("C:/Users/mishrsat/Desktop/Automation/codes")
gelly_auto <- read.csv("CarPrice_Assignment.csv",header = TRUE, sep = ",")
```

Examining the structure of the dataset.

```{r}
str(gelly_auto)
```

Loading the required libraries

```{r warning=FALSE , message=FALSE}
library(MASS)
library(car)
library(tidyr)
library(stringr)
```

**Feature Engineering (PART 1)**

**DUMMY VARIABLE CREATION FOR VARIABLES HAVING TWO OPTIONS**

**Variable - fueltype**

Checking the structure & summary of variable "fueltype"
```{r}
str(gelly_auto$fueltype)
summary(factor(gelly_auto$fueltype))
```

Converting fueltype variable to numeric so as to replace the levels- gas and diesel with 1 and 0
```{r}
levels(gelly_auto$fueltype)<-c(0,1)
```

Storing the numeric values in the same variable
```{r}
gelly_auto$fueltype<- as.numeric(levels(gelly_auto$fueltype))[gelly_auto$fueltype]
```

Checking the summary of variable after conversion
```{r}
summary(factor(gelly_auto$fueltype))
```

**Variable - aspiration**

Checking the structure & summary of variable "aspiration"
```{r}
str(gelly_auto$aspiration)
summary(factor(gelly_auto$aspiration))
```

Converting aspiration variable to numeric so as to replace the levels- std and turbo with 1 and 0
```{r}
levels(gelly_auto$aspiration)<-c(1,0)
```

Storing the numeric values in the same variable
```{r}
gelly_auto$aspiration<- as.numeric(levels(gelly_auto$aspiration))[gelly_auto$aspiration]
```

Checking the summary of variable after conversion
```{r}
summary(factor(gelly_auto$aspiration))
```

**Variable - doornumber**

Checking the structure & summary of variable "doornumber"
```{r}
str(gelly_auto$doornumber)
summary(factor(gelly_auto$doornumber))
```

Converting doornumber variable to numeric so as to replace the levels- four and two with 1 and 0
```{r}
levels(gelly_auto$doornumber)<-c(1,0)
```

Storing the numeric values in the same variable
```{r}
gelly_auto$doornumber<- as.numeric(levels(gelly_auto$doornumber))[gelly_auto$doornumber]
```

Checking the summary of variable after conversion
```{r}
summary(factor(gelly_auto$doornumber))
```

**Variable - enginelocation**

Checking the structure & summary of variable "enginelocation"
```{r}
str(gelly_auto$enginelocation)
summary(factor(gelly_auto$enginelocation))
```

Converting doornumber variable to numeric so as to replace the levels- front and rear with 1 and 0
```{r}
levels(gelly_auto$enginelocation)<-c(1,0)
```

Storing the numeric values in the same variable
```{r}
gelly_auto$enginelocation<- as.numeric(levels(gelly_auto$enginelocation))[gelly_auto$enginelocation]
```

Checking the summary of variable after conversion
```{r}
summary(factor(gelly_auto$enginelocation))
```

**DUMMY VARIABLE CREATION FOR VARIABLES HAVING MORE THAN TWO OPTIONS**

**Variable - carbody**

Checking the summary of variable "carbody"
```{r}
summary(factor(gelly_auto$carbody))
```

Converting "carbody" into dummies
```{r}
carbody_dummy <- data.frame(model.matrix( ~carbody, data = gelly_auto))
```

Removing the x-intercept from the newly created carbody_dummy dataframe,
using the n-1 principal of level creation and keeping the rest 4 variables
```{r}
carbody_dummy <- carbody_dummy[,-1]
```

Merging the dummy variables to the main data set, after removing the original column
```{r}
gelly_auto_carbody <- cbind(gelly_auto[,-7], carbody_dummy)
```

**Variable - drivewheel**

Checking the summary of variable "drivewheel"
```{r}
summary(factor(gelly_auto_carbody$drivewheel))
```

Converting "drivewheel" into dummies
```{r}
drivewheel_dummy <- data.frame(model.matrix( ~drivewheel, data = gelly_auto_carbody))
```

Removing the x-intercept from the newly created drivewheel_dummy dataframe,
using the n-1 principal of level creation and keeping the rest 2 variables
```{r}
drivewheel_dummy <- drivewheel_dummy[,-1]
```

Merging the dummy variables to the main data set, after removing the original column#
```{r}
gelly_auto_drivewheel <- cbind(gelly_auto_carbody[,-7], drivewheel_dummy)
```

**Variable - enginetype**

Checking the summary of variable "enginetype"
```{r}
summary(factor(gelly_auto_drivewheel$enginetype))
```

Converting "enginetype" into dummies
```{r}
enginetype_dummy <- data.frame(model.matrix( ~enginetype, data = gelly_auto_drivewheel))
```

Removing the x-intercept from the newly created enginetype_dummy dataframe,
using the n-1 principal of level creation and keeping the rest 6 variables
```{r}
enginetype_dummy <- enginetype_dummy[,-1]
```

Merging the dummy variables to the main data set, after removing the original column
```{r}
gelly_auto_enginetype <- cbind(gelly_auto_drivewheel[,-13], enginetype_dummy)
```

**Variable - cylindernumber**

Checking the summary of variable "cylindernumber"
```{r}
summary(factor(gelly_auto_enginetype$cylindernumber))
```

Converting "cylindernumber" into dummies
```{r}
cylindernumber_dummy <- data.frame(model.matrix( ~cylindernumber, data = gelly_auto_enginetype))
```

Removing the x-intercept from the newly created cylindernumber_dummy dataframe,
using the n-1 principal of level creation and keeping the rest 6 variables
```{r}
cylindernumber_dummy <- cylindernumber_dummy[,-1]
```

Merging the dummy variables to the main data set, after removing the original column
```{r}
gelly_auto_cylindernumber <- cbind(gelly_auto_enginetype[,-13], cylindernumber_dummy)
```

**Variable - fuelsystem**

Checking the summary of variable "fuelsystem"
```{r}
summary(factor(gelly_auto_cylindernumber$fuelsystem))
```

Converting "fuelsystem" into dummies
```{r}
fuelsystem_dummy <- data.frame(model.matrix( ~fuelsystem, data = gelly_auto_cylindernumber))
```

Removing the x-intercept from the newly created fuelsystem_dummy dataframe,
using the n-1 principal of level creation and keeping the rest 7 variables
```{r}
fuelsystem_dummy <- fuelsystem_dummy[,-1]
```

Merging the dummy variables to the main data set, after removing the original column
```{r}
gelly_auto_fuelsystem <- cbind(gelly_auto_cylindernumber[,-14], fuelsystem_dummy)
```

**Variable - CarName**

**We will first clean up the car name variable, as it has type errors and then go on to build the dummies.**

Separating out the brand and model from "CarName and creating two new variables
```{r warning=FALSE}
gelly_auto_carname <- separate(gelly_auto_fuelsystem,CarName, c("Brand_Name", "Model_Name"), sep = " ", remove = TRUE)
```

Removing the model name column as we do not require it for our analysis
```{r}
gelly_auto_carname <- gelly_auto_carname[,-4]
```

Making all the data in the "Brand_Name" column to proper case
```{r}
gelly_auto_carname$Brand_Name <- str_to_title(gelly_auto_carname$Brand_Name)
```

Checking the summary of variable "Brand_Name"
```{r}
summary(factor(gelly_auto_carname$Brand_Name))
```

Replacing the typo errors in the "Brand_Name" column with the correct name
```{r}
gelly_auto_carname$Brand_Name <- factor(gsub("Maxda", "Mazda", gelly_auto_carname$Brand_Name))
gelly_auto_carname$Brand_Name <- factor(gsub("Vw", "Volkswagen", gelly_auto_carname$Brand_Name))
gelly_auto_carname$Brand_Name <- factor(gsub("Vokswagen", "Volkswagen", gelly_auto_carname$Brand_Name))
gelly_auto_carname$Brand_Name <- factor(gsub("Porcshce", "Porsche", gelly_auto_carname$Brand_Name))
gelly_auto_carname$Brand_Name <- factor(gsub("Toyouta", "Toyota", gelly_auto_carname$Brand_Name))
```

Converting "Brand_Name" into dummies
```{r}
Brand_Name_dummy <- data.frame(model.matrix( ~Brand_Name, data = gelly_auto_carname))
```

Removing the x-intercept from the newly created Brand_Name_dummy dataframe,
using the n-1 principal of level creation and keeping the rest 21 variables
```{r}
Brand_Name_dummy <- Brand_Name_dummy[,-1]
```

Merging the dummy variables to the main data set, after removing the original column
```{r}
gelly_auto_brandname <- cbind(gelly_auto_carname[,-3], Brand_Name_dummy)
```

**Variable - Symboling**

Checking the structure & summary of variable "Symboling"
```{r}
str(gelly_auto_brandname$symboling)
summary(factor(gelly_auto_brandname$symboling))
```

converting the variable to factor
```{r}
gelly_auto_brandname$symboling <- as.factor(gelly_auto_brandname$symboling)
```

Converting "symboling" into dummies
```{r}
symboling_dummy <- data.frame(model.matrix( ~symboling, data = gelly_auto_brandname))
```

Removing the x-intercept from the newly created symboling_dummy dataframe,
using the n-1 principal of level creation and keeping the rest 5 variables
```{r}
symboling_dummy <- symboling_dummy[,-1]
```

Merging the dummy variables to the main data set, after removing the original column
```{r}
gelly_final <- cbind(gelly_auto_brandname[,-2], symboling_dummy)
```

**END OF DUMMY VARIABLE CREATION**

**Removing Variables (PART 2)**

**Removing the variable/s that we do not require for our model building activity**

Removing the "car_ID" column as it just holds unique identifier of each row
```{r}
gelly_final <- gelly_final[-1]
```

**END OF VARIABLE REMOVING PART**

**Model Building (PART 3)**

**Dividing gelly_final into two datasets, train and test datasets**

Setting the seed to 50
```{r}
set.seed(50)
```

Now we randomly generate row indices for train dataset
```{r}
trainindices <- sample(1:nrow(gelly_final), 0.7*nrow(gelly_final))
```

Generating the train data set
```{r}
gelly_train <- gelly_final[trainindices,]
```

Storing the rest of the observations into an object "gelly_test".
```{r}
gelly_test <- gelly_final[-trainindices,]
```

**Model creation begins**

**MODEL 1**

Creating the first multilinear model from the training data set
```{r}
gellymodel_1 <- lm(price~.,data = gelly_train)
```

Checking the summary of model 
```{r}
summary(gellymodel_1)
```

Using the step AIC function to quickly remove the variables that are not significant for the calculation

Please Note :- As the output for this step is quite big, we will not show the output here.
```{r results = "hide"}
gelly_step <- stepAIC(gellymodel_1, direction = "both")
```

After using the step AIC methodology, calling the dataset to understand, what are the remaining variable on which subsequent model/s can be created
```{r}
gelly_step
```

From now on we will be looking at two statistical measures to eliminate variables manually

* Variance Inflation Factor (VIF) - This quantifies the severity of multicollinearity in a ordinary least square method
* P-value - Helps you understand the significance of a variable, p-value should be less 0.05 for a variable to be significant

We will be eliminating variables that have a high VIF and p-value > 0.05

**MODEL 2**

Creating the 2nd Model after executing the above mentioned step AIC
```{r}
gellymodel_2 <- lm(formula = price ~ fueltype + aspiration + enginelocation + 
                     wheelbase + carlength + carwidth + carheight + curbweight + 
                     enginesize + boreratio + stroke + peakrpm + citympg + carbodyhardtop + 
                     carbodyhatchback + carbodysedan + carbodywagon + drivewheelfwd + 
                     drivewheelrwd + enginetypel + enginetypeohc + enginetypeohcf + 
                     enginetypeohcv + enginetyperotor + cylindernumberfour + cylindernumberthree + 
                     fuelsystem2bbl + fuelsystemmpfi + Brand_NameAudi + Brand_NameBmw + 
                     Brand_NameBuick + Brand_NameDodge + Brand_NameMazda + Brand_NameMitsubishi + 
                     Brand_NameNissan + Brand_NamePlymouth + Brand_NamePorsche + 
                     Brand_NameSaab + symboling2 + symboling3, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_2)
```

Passing the model into the vif function
```{r}
vif(gellymodel_2)
```

**MODEL 3**

* Removing drivewheelrwd variable based on High VIF and insignificance (p>0.05)
* Making a new model without drivewheelrwd variable

Creating the 3rd Model without the above mentioned field
```{r}
gellymodel_3 <- lm(formula = price ~ fueltype + aspiration + enginelocation + 
                     wheelbase + carlength + carwidth + carheight + curbweight + 
                     enginesize + boreratio + stroke + peakrpm + citympg + carbodyhardtop + 
                     carbodyhatchback + carbodysedan + carbodywagon + drivewheelfwd + 
                     enginetypel + enginetypeohc + enginetypeohcf + 
                     enginetypeohcv + enginetyperotor + cylindernumberfour + cylindernumberthree + 
                     fuelsystem2bbl + fuelsystemmpfi + Brand_NameAudi + Brand_NameBmw + 
                     Brand_NameBuick + Brand_NameDodge + Brand_NameMazda + Brand_NameMitsubishi + 
                     Brand_NameNissan + Brand_NamePlymouth + Brand_NamePorsche + 
                     Brand_NameSaab + symboling2 + symboling3, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_3)
```

Passing the model into the vif function
```{r}
vif(gellymodel_3)
```

**MODEL 4**

* Removing drivewheelfwd variable based on High VIF and insignificance (p>0.05)
* Making a new model without drivewheelfwd variable

Creating the 4th Model without the above mentioned fields
```{r}
gellymodel_4 <- lm(formula = price ~ fueltype + aspiration + enginelocation + 
                     wheelbase + carlength + carwidth + carheight + curbweight + 
                     enginesize + boreratio + stroke + peakrpm + citympg + carbodyhardtop + 
                     carbodyhatchback + carbodysedan + carbodywagon +  
                     enginetypel + enginetypeohc + enginetypeohcf + 
                     enginetypeohcv + enginetyperotor + cylindernumberfour + cylindernumberthree + 
                     fuelsystem2bbl + fuelsystemmpfi + Brand_NameAudi + Brand_NameBmw + 
                     Brand_NameBuick + Brand_NameDodge + Brand_NameMazda + Brand_NameMitsubishi + 
                     Brand_NameNissan + Brand_NamePlymouth + Brand_NamePorsche + 
                     Brand_NameSaab + symboling2 + symboling3, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_4)
```

Passing the model into the vif function
```{r}
vif(gellymodel_4)
```

**MODEL 5**

* Removing citympg variable based on High VIF and insignificance (p>0.05)
* Making a new model without citympg variable

Creating the 5th Model without the above mentioned fields
```{r}
gellymodel_5 <- lm(formula = price ~ fueltype + aspiration + enginelocation + 
                     wheelbase + carlength + carwidth + carheight + curbweight + 
                     enginesize + boreratio + stroke + peakrpm + carbodyhardtop + 
                     carbodyhatchback + carbodysedan + carbodywagon +  
                     enginetypel + enginetypeohc + enginetypeohcf + 
                     enginetypeohcv + enginetyperotor + cylindernumberfour + cylindernumberthree + 
                     fuelsystem2bbl + fuelsystemmpfi + Brand_NameAudi + Brand_NameBmw + 
                     Brand_NameBuick + Brand_NameDodge + Brand_NameMazda + Brand_NameMitsubishi + 
                     Brand_NameNissan + Brand_NamePlymouth + Brand_NamePorsche + 
                     Brand_NameSaab + symboling2 + symboling3, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_5)
```

Passing the model into the vif function
```{r}
vif(gellymodel_5)
```

**MODEL 6**

* Removing Brand_NameMazda variable based on High VIF and insignificance (p>0.05)
* Making a new model without Brand_NameMazda variable

Creating the 6th Model without the above mentioned fields
```{r}
gellymodel_6 <- lm(formula = price ~ fueltype + aspiration + enginelocation + 
                     wheelbase + carlength + carwidth + carheight + curbweight + 
                     enginesize + boreratio + stroke + peakrpm + carbodyhardtop + 
                     carbodyhatchback + carbodysedan + carbodywagon +  
                     enginetypel + enginetypeohc + enginetypeohcf + 
                     enginetypeohcv + enginetyperotor + cylindernumberfour + cylindernumberthree + 
                     fuelsystem2bbl + fuelsystemmpfi + Brand_NameAudi + Brand_NameBmw + 
                     Brand_NameBuick + Brand_NameDodge + Brand_NameMitsubishi + 
                     Brand_NameNissan + Brand_NamePlymouth + Brand_NamePorsche + 
                     Brand_NameSaab + symboling2 + symboling3, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_6)
```

Passing the model into the vif function
```{r}
vif(gellymodel_6)
```

**MODEL 7**

* Removing Brand_NameNissan variable based on High VIF and insignificance (p>0.05)
* Making a new model without Brand_NameNissan variable

Creating the 7th Model without the above mentioned fields
```{r}
gellymodel_7 <- lm(formula = price ~ fueltype + aspiration + enginelocation + 
                     wheelbase + carlength + carwidth + carheight + curbweight + 
                     enginesize + boreratio + stroke + peakrpm + carbodyhardtop + 
                     carbodyhatchback + carbodysedan + carbodywagon +  
                     enginetypel + enginetypeohc + enginetypeohcf + 
                     enginetypeohcv + enginetyperotor + cylindernumberfour + cylindernumberthree + 
                     fuelsystem2bbl + fuelsystemmpfi + Brand_NameAudi + Brand_NameBmw + 
                     Brand_NameBuick + Brand_NameDodge + Brand_NameMitsubishi + 
                     Brand_NamePlymouth + Brand_NamePorsche + 
                     Brand_NameSaab + symboling2 + symboling3, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_7)
```

Passing the model into the vif function
```{r}
vif(gellymodel_7)
```

**MODEL 8**

* Removing symboling2 variable based on High VIF and insignificance (p>0.05)
* Making a new model without symboling2 variable

Creating the 8th Model without the above mentioned fields
```{r}
gellymodel_8 <- lm(formula = price ~ fueltype + aspiration + enginelocation + 
                     wheelbase + carlength + carwidth + carheight + curbweight + 
                     enginesize + boreratio + stroke + peakrpm + carbodyhardtop + 
                     carbodyhatchback + carbodysedan + carbodywagon +  
                     enginetypel + enginetypeohc + enginetypeohcf + 
                     enginetypeohcv + enginetyperotor + cylindernumberfour + cylindernumberthree + 
                     fuelsystem2bbl + fuelsystemmpfi + Brand_NameAudi + Brand_NameBmw + 
                     Brand_NameBuick + Brand_NameDodge + Brand_NameMitsubishi + 
                     Brand_NamePlymouth + Brand_NamePorsche + 
                     Brand_NameSaab + symboling3, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_8)
```

Passing the model into the vif function
```{r}
vif(gellymodel_8)
```

**MODEL 9**

* Removing carlength variable based on High VIF and insignificance (p>0.05)
* Making a new model without carlength variable

Creating the 9th Model without the above mentioned fields
```{r}
gellymodel_9 <- lm(formula = price ~ fueltype + aspiration + enginelocation + 
                     wheelbase + carwidth + carheight + curbweight + 
                     enginesize + boreratio + stroke + peakrpm + carbodyhardtop + 
                     carbodyhatchback + carbodysedan + carbodywagon +  
                     enginetypel + enginetypeohc + enginetypeohcf + 
                     enginetypeohcv + enginetyperotor + cylindernumberfour + cylindernumberthree + 
                     fuelsystem2bbl + fuelsystemmpfi + Brand_NameAudi + Brand_NameBmw + 
                     Brand_NameBuick + Brand_NameDodge + Brand_NameMitsubishi + 
                     Brand_NamePlymouth + Brand_NamePorsche + 
                     Brand_NameSaab + symboling3, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_9)
```

Passing the model into the vif function
```{r}
vif(gellymodel_9)
```

**MODEL 10**

* Removing wheelbase variable based on High VIF and insignificance (p>0.05)
* Making a new model without wheelbase variable

Creating the 10th Model without the above mentioned fields
```{r}
gellymodel_10 <- lm(formula = price ~ fueltype + aspiration + enginelocation + 
                     carwidth + carheight + curbweight + 
                     enginesize + boreratio + stroke + peakrpm + carbodyhardtop + 
                     carbodyhatchback + carbodysedan + carbodywagon +  
                     enginetypel + enginetypeohc + enginetypeohcf + 
                     enginetypeohcv + enginetyperotor + cylindernumberfour + cylindernumberthree + 
                     fuelsystem2bbl + fuelsystemmpfi + Brand_NameAudi + Brand_NameBmw + 
                     Brand_NameBuick + Brand_NameDodge + Brand_NameMitsubishi + 
                     Brand_NamePlymouth + Brand_NamePorsche + 
                     Brand_NameSaab + symboling3, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_10)
```

Passing the model into the vif function
```{r}
vif(gellymodel_10)
```

**MODEL 11**

* Removing enginetypel variable based on High VIF and insignificance (p>0.05)
* Making a new model without enginetypel variable

Creating the 11th Model without the above mentioned fields
```{r}
gellymodel_11 <- lm(formula = price ~ fueltype + aspiration + enginelocation + 
                      carwidth + carheight + curbweight + 
                      enginesize + boreratio + stroke + peakrpm + carbodyhardtop + 
                      carbodyhatchback + carbodysedan + carbodywagon +  
                      enginetypeohc + enginetypeohcf + 
                      enginetypeohcv + enginetyperotor + cylindernumberfour + cylindernumberthree + 
                      fuelsystem2bbl + fuelsystemmpfi + Brand_NameAudi + Brand_NameBmw + 
                      Brand_NameBuick + Brand_NameDodge + Brand_NameMitsubishi + 
                      Brand_NamePlymouth + Brand_NamePorsche + 
                      Brand_NameSaab + symboling3, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_11)
```

Passing the model into the vif function
```{r}
vif(gellymodel_11)
```

**MODEL 12**

* Removing carheight variable based on High VIF and insignificance (p>0.05)
* Making a new model without carheight variable

Creating the 12th Model without the above mentioned fields
```{r}
gellymodel_12 <- lm(formula = price ~ fueltype + aspiration + enginelocation + 
                      carwidth + curbweight + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhardtop + carbodyhatchback + carbodysedan + 
                      carbodywagon + enginetypeohc + enginetypeohcf +  
                      enginetypeohcv + enginetyperotor + cylindernumberfour +  
                      cylindernumberthree + fuelsystem2bbl + fuelsystemmpfi + 
                      Brand_NameAudi + Brand_NameBmw + Brand_NameBuick + Brand_NameDodge + 
                      Brand_NameMitsubishi + Brand_NamePlymouth + Brand_NamePorsche +
                      Brand_NameSaab + symboling3, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_12)
```

Passing the model into the vif function
```{r}
vif(gellymodel_12)
```

**MODEL 13**

* Removing symboling3 variable based on High VIF and insignificance (p>0.05)
* Making a new model without symboling3 variable

Creating the 13th Model without the above mentioned fields
```{r}
gellymodel_13 <- lm(formula = price ~ fueltype + aspiration + enginelocation + 
                      carwidth + curbweight + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhardtop + carbodyhatchback + carbodysedan + 
                      carbodywagon + enginetypeohc + enginetypeohcf +  
                      enginetypeohcv + enginetyperotor + cylindernumberfour +  
                      cylindernumberthree + fuelsystem2bbl + fuelsystemmpfi + 
                      Brand_NameAudi + Brand_NameBmw + Brand_NameBuick + Brand_NameDodge + 
                      Brand_NameMitsubishi + Brand_NamePlymouth + Brand_NamePorsche +
                      Brand_NameSaab, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_13)
```

Passing the model into the vif function
```{r}
vif(gellymodel_13)
```

**MODEL 14**

* Removing Brand_NameAudi variable based on High VIF and insignificance (p>0.05)
* Making a new model without Brand_NameAudi variable

Creating the 14th Model without the above mentioned fields
```{r}
gellymodel_14 <- lm(formula = price ~ fueltype + aspiration + enginelocation + 
                      carwidth + curbweight + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhardtop + carbodyhatchback + carbodysedan + 
                      carbodywagon + enginetypeohc + enginetypeohcf +  
                      enginetypeohcv + enginetyperotor + cylindernumberfour +  
                      cylindernumberthree + fuelsystem2bbl + fuelsystemmpfi + 
                      Brand_NameBmw + Brand_NameBuick + Brand_NameDodge + 
                      Brand_NameMitsubishi + Brand_NamePlymouth + Brand_NamePorsche +
                      Brand_NameSaab, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_14)
```

Passing the model into the vif function
```{r}
vif(gellymodel_14)
```

**MODEL 15**

* Removing Brand_NameSaab variable based on High VIF and insignificance (p>0.05)
* Making a new model without Brand_NameSaab variable

Creating the 15th Model without the above mentioned fields
```{r}
gellymodel_15 <- lm(formula = price ~ fueltype + aspiration + enginelocation + 
                      carwidth + curbweight + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhardtop + carbodyhatchback + carbodysedan + 
                      carbodywagon + enginetypeohc + enginetypeohcf +  
                      enginetypeohcv + enginetyperotor + cylindernumberfour +  
                      cylindernumberthree + fuelsystem2bbl + fuelsystemmpfi + 
                      Brand_NameBmw + Brand_NameBuick + Brand_NameDodge + 
                      Brand_NameMitsubishi + Brand_NamePlymouth + 
                      Brand_NamePorsche, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_15)
```

Passing the model into the vif function
```{r}
vif(gellymodel_15)
```

**MODEL 16**

* Removing fueltype variable based on High VIF and insignificance (p>0.05)
* Making a new model without fueltype variable

Creating the 16th Model without the above mentioned fields
```{r}
gellymodel_16 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + curbweight + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhardtop + carbodyhatchback + carbodysedan + 
                      carbodywagon + enginetypeohc + enginetypeohcf +  
                      enginetypeohcv + enginetyperotor + cylindernumberfour +  
                      cylindernumberthree + fuelsystem2bbl + fuelsystemmpfi + 
                      Brand_NameBmw + Brand_NameBuick + Brand_NameDodge + 
                      Brand_NameMitsubishi + Brand_NamePlymouth + 
                      Brand_NamePorsche, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_16)
```

Passing the model into the vif function
```{r}
vif(gellymodel_16)
```

**MODEL 17**

* Removing fuelsystemmpfi variable based on High VIF and insignificance (p>0.05)
* Making a new model without fuelsystemmpfi variable

Creating the 17th Model without the above mentioned fields
```{r}
gellymodel_17 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + curbweight + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhardtop + carbodyhatchback + carbodysedan + 
                      carbodywagon + enginetypeohc + enginetypeohcf +  
                      enginetypeohcv + enginetyperotor + cylindernumberfour +  
                      cylindernumberthree + fuelsystem2bbl + 
                      Brand_NameBmw + Brand_NameBuick + Brand_NameDodge + 
                      Brand_NameMitsubishi + Brand_NamePlymouth + 
                      Brand_NamePorsche, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_17)
```

Passing the model into the vif function
```{r}
vif(gellymodel_17)
```

**MODEL 18**

* Removing enginetypeohcf variable based on High VIF and insignificance (p>0.05)
* Making a new model without enginetypeohcf variable

Creating the 18th Model without the above mentioned fields
```{r}
gellymodel_18 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + curbweight + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhardtop + carbodyhatchback + carbodysedan + 
                      carbodywagon + enginetypeohc + enginetypeohcv + enginetyperotor +   
                      cylindernumberfour + cylindernumberthree + fuelsystem2bbl +  
                      Brand_NameBmw + Brand_NameBuick + Brand_NameDodge + 
                      Brand_NameMitsubishi + Brand_NamePlymouth + 
                      Brand_NamePorsche, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_18)
```

Passing the model into the vif function
```{r}
vif(gellymodel_18)
```

**MODEL 19**

* Removing fuelsystem2bbl variable based on High VIF and insignificance (p>0.05)
* Making a new model without fuelsystem2bbl variable

Creating the 19th Model without the above mentioned fields
```{r}
gellymodel_19 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + curbweight + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhardtop + carbodyhatchback + carbodysedan + 
                      carbodywagon + enginetypeohc + enginetypeohcv + enginetyperotor +   
                      cylindernumberfour + cylindernumberthree +   
                      Brand_NameBmw + Brand_NameBuick + Brand_NameDodge + 
                      Brand_NameMitsubishi + Brand_NamePlymouth + 
                      Brand_NamePorsche, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_19)
```

Passing the model into the vif function
```{r}
vif(gellymodel_19)
```

**MODEL 20**

* Removing Brand_NameDodge variable based on High VIF and insignificance (p>0.05)
* Making a new model without Brand_NameDodge variable

Creating the 20th Model without the above mentioned fields
```{r}
gellymodel_20 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + curbweight + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhardtop + carbodyhatchback + carbodysedan + 
                      carbodywagon + enginetypeohc + enginetypeohcv + enginetyperotor +   
                      cylindernumberfour + cylindernumberthree +   
                      Brand_NameBmw + Brand_NameBuick +  
                      Brand_NameMitsubishi + Brand_NamePlymouth + 
                      Brand_NamePorsche, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_20)
```

Passing the model into the vif function
```{r}
vif(gellymodel_20)
```

**MODEL 21**

* Removing Brand_NamePlymouth variable based on High VIF and insignificance (p>0.05)
* Making a new model without Brand_NamePlymouth variable

Creating the 21st Model without the above mentioned fields
```{r}
gellymodel_21 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + curbweight + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhardtop + carbodyhatchback + carbodysedan + 
                      carbodywagon + enginetypeohc + enginetypeohcv + enginetyperotor +   
                      cylindernumberfour + cylindernumberthree +   
                      Brand_NameBmw + Brand_NameBuick +  
                      Brand_NameMitsubishi + Brand_NamePorsche, data = gelly_train)
```


Checking the summary of model
```{r}
summary(gellymodel_21)
```

Passing the model into the vif function
```{r}
vif(gellymodel_21)
```

**MODEL 22**

* Removing cylindernumberfour variable based on High VIF and insignificance (p>0.05)
* Making a new model without cylindernumberfour variable

Creating the 22nd Model without the above mentioned fields
```{r}
gellymodel_22 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + curbweight + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhardtop + carbodyhatchback + carbodysedan + 
                      carbodywagon + enginetypeohc + enginetypeohcv + enginetyperotor +   
                      cylindernumberthree + Brand_NameBmw + Brand_NameBuick +  
                      Brand_NameMitsubishi + Brand_NamePorsche, data = gelly_train)
```

Checking the summary of model
```{r}
summary(gellymodel_22)
```

Passing the model into the vif function
```{r}
vif(gellymodel_22)
```

**MODEL 23**

* Removing enginetypeohcv variable based on High VIF and insignificance (p>0.05)
* Making a new model without enginetypeohcv variable

Creating the 23rd Model without the above mentioned fields
```{r}
gellymodel_23 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + curbweight + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhardtop + carbodyhatchback + carbodysedan + 
                      carbodywagon + enginetypeohc + enginetyperotor +   
                      cylindernumberthree + Brand_NameBmw + Brand_NameBuick +  
                      Brand_NameMitsubishi + Brand_NamePorsche, data = gelly_train)
```


Checking the summary of model
```{r}
summary(gellymodel_23)
```

Passing the model into the vif function
```{r}
vif(gellymodel_23)
```

**MODEL 24**

* Removing curbweight variable based on High VIF and insignificance (p>0.05)
* Making a new model without curbweight variable

Creating the 24th Model without the above mentioned fields
```{r}
gellymodel_24 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhardtop + carbodyhatchback + carbodysedan + 
                      carbodywagon + enginetypeohc + enginetyperotor +   
                      cylindernumberthree + Brand_NameBmw + Brand_NameBuick +  
                      Brand_NameMitsubishi + Brand_NamePorsche, data = gelly_train)
```


Checking the summary of model
```{r}
summary(gellymodel_24)
```

Passing the model into the vif function
```{r}
vif(gellymodel_24)
```

**MODEL 25**

* Removing carbodywagon variable based on High VIF and insignificance (p>0.05)
* Making a new model without carbodywagon variable

Creating the 25th Model without the above mentioned fields
```{r}
gellymodel_25 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhardtop + carbodyhatchback + carbodysedan + 
                      enginetypeohc + enginetyperotor +   
                      cylindernumberthree + Brand_NameBmw + Brand_NameBuick +  
                      Brand_NameMitsubishi + Brand_NamePorsche, data = gelly_train)
```


Checking the summary of model
```{r}
summary(gellymodel_25)
```

Passing the model into the vif function
```{r}
vif(gellymodel_25)
```

**MODEL 26**

* Removing carbodysedan variable based on High VIF and insignificance (p>0.05)
* Making a new model without carbodysedan variable

Creating the 26th Model without the above mentioned fields
```{r}
gellymodel_26 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhardtop + carbodyhatchback + 
                      enginetypeohc + enginetyperotor +   
                      cylindernumberthree + Brand_NameBmw + Brand_NameBuick +  
                      Brand_NameMitsubishi + Brand_NamePorsche, data = gelly_train)
```


Checking the summary of model
```{r}
summary(gellymodel_26)
```

Passing the model into the vif function
```{r}
vif(gellymodel_26)
```

**MODEL 27**

* Removing carbodyhardtop variable based on High VIF and insignificance (p>0.05)
* Making a new model without carbodyhardtop variable

Creating the 27th Model without the above mentioned fields
```{r}
gellymodel_27 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhatchback + 
                      enginetypeohc + enginetyperotor +   
                      cylindernumberthree + Brand_NameBmw + Brand_NameBuick +  
                      Brand_NameMitsubishi + Brand_NamePorsche, data = gelly_train)
```


Checking the summary of model
```{r}
summary(gellymodel_27)
```

Passing the model into the vif function
```{r}
vif(gellymodel_27)
```

**MODEL 28**

* Removing Brand_NameMitsubishi variable based on High VIF and insignificance (p>0.05)
* Making a new model without Brand_NameMitsubishi variable

Creating the 28th Model without the above mentioned fields
```{r}
gellymodel_28 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhatchback + 
                      enginetypeohc + enginetyperotor +   
                      cylindernumberthree + Brand_NameBmw + Brand_NameBuick +  
                      Brand_NamePorsche, data = gelly_train)
```


Checking the summary of model
```{r}
summary(gellymodel_28)
```

Passing the model into the vif function
```{r}
vif(gellymodel_28)
```

**MODEL 29**

* Removing Brand_NamePorsche variable based on High VIF and insignificance (p>0.05)
* Making a new model without Brand_NamePorsche variable

Creating the 29th Model without the above mentioned fields
```{r}
gellymodel_29 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + enginesize + boreratio + stroke + 
                      peakrpm + carbodyhatchback + 
                      enginetypeohc + enginetyperotor + cylindernumberthree +   
                      Brand_NameBmw + Brand_NameBuick, data = gelly_train) 
```
                 

Checking the summary of model
```{r}
summary(gellymodel_29)
```

Passing the model into the vif function
```{r}
vif(gellymodel_29)
```

**MODEL 30**

* Removing carbodyhatchback variable based on High VIF and insignificance (p>0.05)
* Making a new model without carbodyhatchback variable

Creating the 30th Model without the above mentioned fields
```{r}
gellymodel_30 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + enginesize + boreratio + stroke + 
                      peakrpm + enginetypeohc + enginetyperotor + cylindernumberthree +
                      Brand_NameBmw + Brand_NameBuick, data = gelly_train) 
```


Checking the summary of model
```{r}
summary(gellymodel_30)
```

Passing the model into the vif function
```{r}
vif(gellymodel_30)
```

**MODEL 31**

* Removing boreratio variable based on High VIF and insignificance (p>0.05)
* Making a new model without boreratio variable

Creating the 31st Model without the above mentioned fields
```{r}
gellymodel_31 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + enginesize + stroke + 
                      peakrpm + enginetypeohc + enginetyperotor + cylindernumberthree +
                      Brand_NameBmw + Brand_NameBuick, data = gelly_train) 
```


Checking the summary of model
```{r}
summary(gellymodel_31)
```

Passing the model into the vif function
```{r}
vif(gellymodel_31)
```

**MODEL 32**

* Removing enginetypeohc variable based on High VIF and insignificance (p>0.05)
* Making a new model without enginetypeohc variable

Creating the 32nd Model without the above mentioned fields
```{r}
gellymodel_32 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + enginesize + stroke + 
                      peakrpm + enginetyperotor + cylindernumberthree +
                      Brand_NameBmw + Brand_NameBuick, data = gelly_train) 
```


Checking the summary of model
```{r}
summary(gellymodel_32)
```

Passing the model into the vif function
```{r}
vif(gellymodel_32)
```

**MODEL 33**

* Removing cylindernumberthree variable based on High VIF and insignificance (p>0.05)
* Making a new model without cylindernumberthree variable

Creating the 33rd Model without the above mentioned fields
```{r}
gellymodel_33 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + enginesize + stroke + 
                      peakrpm + enginetyperotor + 
                      Brand_NameBmw + Brand_NameBuick, data = gelly_train) 
```


Checking the summary of model
```{r}
summary(gellymodel_33)
```

Passing the model into the vif function
```{r}
vif(gellymodel_33)
```

**MODEL 34**

* Removing Brand_NameBmw, Brand_NameBuick variable as they were making the model more rigid
* Making a new model without Brand_NameBmw, Brand_NameBuick variable

Creating the 34th Model without the above mentioned fields
```{r}
gellymodel_34 <- lm(formula = price ~ aspiration + enginelocation + 
                      carwidth + enginesize + stroke + 
                      peakrpm + enginetyperotor, data = gelly_train)
```


Checking the summary of model
```{r}
summary(gellymodel_34)
```

Passing the model into the vif function
```{r}
vif(gellymodel_34)
```

**MODEL 35**

* Removing aspiration variable based on High VIF
* Making a new model without aspiration variable

Creating the 35th Model without the above mentioned fields
```{r}
gellymodel_35 <- lm(formula = price ~ enginelocation + 
                      carwidth + enginesize + stroke + 
                      peakrpm + enginetyperotor, data = gelly_train)
```


Checking the summary of model
```{r}
summary(gellymodel_35)
```

Passing the model into the vif function
```{r}
vif(gellymodel_35)
```

**The final training model will consist of enginelocation, carwidth, enginesize, stroke, peakrpm and enginetyperotor. Only these 6 variables with an adjusted r square of 0.8606 and r square of 0.8665**

**END OF MODEL BUILDING PART**

**Model Evaluation (PART 4)**

Predicting the car prices with the testing dataset

We will be using MODEL 35 to do the prediction
```{r}
gellyPredict <- predict(gellymodel_35,gelly_test[,-18])
gelly_test$predicted_price <- gellyPredict
```

calculating the correlation to find the accuracy of predicted values
```{r}
r_value <- cor(gelly_test$price,gelly_test$predicted_price)
```

We see that the r value is 0.93822, now we will calculate the r-square
```{r}
rsquared_value <- cor(gelly_test$price,gelly_test$predicted_price)^2
```

We see that the r squared value comes to 0.88026 which when compared to the training model_35's r square, seems to be pretty close

**END OF MODEL EVALUATION PART**

**CONCLUSION**

Hence we can conclude that the r square for both training set and testing data seems to be pretty close, which tells us that this model is good to go. The final variables that were the most significant while predicting the price in which gelly auto should launch its product were enginelocation, carwidth, enginesize, stroke, peakrpm and enginetyperotor.

**IF YOU HAVE REACHED HERE, THEN BY NOW YOU KNOW HOW TO EXECUTE A LINEAR REGRESSION ALGO USING THE ORDINARY LEAST SQUARE METHOD**











